\sysfull

### 2018-04-16 paper/evaluation.tex
Working on evaluation text

Our evaluation illustrates key findings about \sys. We show that: \todo{Make a list of core findings here once results are solid}{Przemek}

\subsection{\sys Runtime Performance}
\label{sec:results_evaluation}

Our aim is to assess \sys as detailed as possible. For this we have characterized \sys runtime performance (execution time), based on a set of benchmarks, considering core task adaptation mechanisms of \sys: \emph{task coalescing} and \emph{task downscaling}. We also characterize \sys overhead showing precisely what is the source of \sys superior performance. Additionally, we characterize \sys code.

\sys is compared to Alpaca runtime. We remind the reader that the benchmarks for Alpaca were hand-transformed in a time-consuming manual process from Clang (LLVM-generated code) to GCC (see Section~\ref{sec:implementation}). The manual code transformation was required as \sys was written with GCC in mind, and Alpaca cannot support any other complier than LLVM.

\subsubsection{\sys Task Adaptation}
\label{sec:result_coalescing}

@@

\subsubsection{Characterization of \sys Overhead}
\label{sec:coala_overhead}

\indent \textbf{Overall \sys Overhead Breakdown.} The result is presented in Figure~\ref{fig:overallOverheadBreakdown}.

\todo{replace slow coalescing with steady coalescing}{Przemek}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/overallOverhead}
	\caption{Overall \sys overhead breakdown; NC: no coalescing, SC: slow coalescing, EA: energy-aware coalescing.}
	\label{fig:overallOverheadBreakdown}
\end{figure}

\textbf{\sys Coalescing Algorithm Efficiency.} The result is presented in Figure~\ref{fig:coalEfficiency}.

Fixed power or intermittent?

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalEfficiency}
	\caption{\sys coalescing algorithm efficiency; NC: no coalescing, SC: slow coalescing, EA: energy-aware coalescing, ETA: energy and task-aware coalescing.}
	\label{fig:coalEfficiency}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/memAccess}
	\caption{\sys memory access overhead breakdown; nc: no coalescing, sc: slow coalescing, ea: energy-aware coalescing.}
	\label{fig:coalmemory}
\end{figure}

\subsubsection{\sys Paging Performance}
\label{sec:results_memory_management}

>>>>

\begin{wrapfigure}{t!}{0.5\textwidth}
	%\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/coalEfficiency}
	\caption{Normalized \sys runtime for all coalescing strategies compared to non-coalesced \sys with overall \sys overhead breakdown; NC: no coalescing, EB: energy-blind coalescing, EA: energy-aware coalescing, ETA: energy and task-aware coalescing. All \sys coalescing strategies significantly reduce the overhead of (task) commits. EA and ETA perform much better than EB a they reduce re-execution further.}
	\label{fig:overallOverheadBreakdown}
	%\end{figure}
\end{wrapfigure}

Our results illustrate key findings about \sys. We show through extensive qualitative and quantitative evaluation that (i) \sys \emph{provides computation progress} at the partial task level, guaranteeing execution at the worst intermittent energy conditions where state-of-the-art runtimes fail; (ii) usually \emph{improve execution speed} of applications compared to the state-of-the-art runtimes; (iii) \sys through coalescing mechanism \emph{reduces the memory protection overhead} significantly; and (iv) that \sys is \emph{more generic to use} and allows to interact with code written for non-intermittent devices much easier.

\textbf{Key Performance Indicators.} Our aim is to assess \sys as detailed as possible. For this we have characterized \sys runtime performance (execution time), based on a set of benchmarks, considering core task adaptation mechanisms of \sys: \emph{task coalescing} and \emph{task downscaling}. We also characterize \sys overhead showing precisely what is the source of \sys superior performance investigating task re-execution and commit penalty and memory page access patterns.

We remind the reader that \sys is compared to Alpaca runtime and the benchmarks for Alpaca were hand-transformed in a time-consuming manual process from Clang (LLVM-generated code) to GCC (see Section~\ref{sec:implementation}). The manual code transformation was required as \sys was written with GCC in mind, and Alpaca cannot support any other complier than LLVM.

\subsection{Characterization of \sys Overhead}
\label{sec:coala_overhead}

We start with the assessment of \sys Overhead for all benchmarks. This will lead us to the selection of the best set of coalescing strategies.

\indent \textbf{\sys Coalescing Algorithm Efficiency.} We have measured the time spent on executing (i) user code, (ii) task re-execution and (iii) task commits for all coalescing strategies (EB, EA, and ETA) and all benchmarks. We compared our results to non-coalescing \sys (NC). The experiment was performed at 15\,cm WISP to RF generator antenna distance and normalized \todo{to what}{Przemek}. The result is presented in Figure~\ref{fig:overallOverheadBreakdown}. We clearly see that any \sys coalescing strategy reduces the cost of task commit for \emph{all} benchmarks. EA and ETA strategies reduce the re-execution cost of tasks further. For this reason we proceed with the investigation of \sys without considering EB coalescing.

\textbf{Overall \sys Overhead Breakdown.} The result is presented in Figure~\ref{fig:coalEfficiency}.

\begin{figure}
	\centering
	\includegraphics[width=0.49\columnwidth]{figures/overallOverhead}
	\includegraphics[width=0.49\columnwidth]{figures/memAccess}
	\caption{\sys coalescing algorithm efficiency; NC: no coalescing, EA: energy-aware coalescing, ETA: energy and task-aware coalescing. Left: normalized runtime, Right: memory access breakdown.}
	\label{fig:coalEfficiency}
\end{figure}

%\begin{figure}
%	\centering
%	\includegraphics[width=\columnwidth]{figures/memAccess}
%	\caption{\sys memory access overhead breakdown; nc: no coalescing, sc: slow coalescing, ea: energy-aware coalescing.}
%	\label{fig:coalmemory}
%\end{figure}

\subsection{\sys Task Adaptation}
\label{sec:result_coalescing}

@@

\subsection{\sys Paging Performance}
\label{sec:results_memory_management}
